---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# QregBB

<!-- badges: start -->
<!-- badges: end -->

The R package QregBB accompanies the paper: 

Gregory, K.B., Lahiri, S.N., Nordman, D.J. (2018). A smooth block bootstrap for quantile regression with time series. *Annals of Statistics* 46(3), 1138-1166

Find the paper at https://projecteuclid.org/euclid.aos/1525313078.

## Installation

You can install the development version of QregBB from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gregorkb/QregBB")
```

## Example

The main function in the package is `QregBB`, which performs the MBB, SMBB, ETBB, and SETBB bootstrap procedures (all at once) for estimating the sampling distributions of quantile regression estimators with time series data. 

```{r QregBB_example}
library(QregBB)

n <- 50
X1 <- arima.sim(model=list(ar=c(.7,.1)),n)
X2 <- arima.sim(model=list(ar=c(.2,.1)),n)
e <- arima.sim(model=list(ar=c(.7,.1)),n)
Y <- X1 + e
X <- cbind(rep(1,n),X1,X2)
QregBB.out <- QregBB(Y,X,tau=.5,l=4,B=500,h=NULL,alpha=0.05)

QregBB.out
```

The function `getNPPIblksizesQR` implements the block size selection method described in Gregory et al. (2018) for MBB, SMBB, ETBB, and SETBB.

```{r getNPPIblksizesQR_example}
blksize.out <- getNPPIblksizesQR(Y,X,tau=.5)
blksize.out
```
<!--
You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
-->